Examining Crowd Work and Gig Work Through The Historical Lens of Piecework

### 2017-05-10 chi/piecework/presentation/complexity.tex
checkin with most of the bolded/critical fixes resolved (see main page)

\section{Complexity}

\begin{frame}{Complexity}
  What do we mean when we talk about complexity?
  % \begin{minipage}[t][25mm][t]{\textwidth}
  %   \begin{columns}
  %     \begin{column}[T]{0.8\textwidth}
        \begin{itemize}
          \item<1->
          Can crowds help you write something?\\
          \scriptsize{\textcite{bernsteinSoylent,Kim:2014:CSI:2556288.2556986,Nebeling:2016:WCW:2858036.2858169}}\normalsize{}
          \item<2-> Can crowds critique novel designs?\\
          \scriptsize{\textcite{yuanAlmost,fuge2014analysis}}\normalsize{}
          \item<3-> Can crowds create things from whole cloth?\\
          \scriptsize{\textcite{KimStoria,Kim2017,Hahn:2016:KAB:2858036.2858364,Lasecki:2014:LSR:2661334.2661352}}\normalsize{}
        \end{itemize}
      % \end{column}
      % \begin{column}[T]{0.2\textwidth}
      %   \begin{figure}
    % \centering
    % \vspace{0mm}

    % \visible<1->{\includegraphics[width=.33\textwidth]{figures/complexity/geodesic.png}}%
    % \visible<3->{
    % \includegraphics<1->[width=.5\textwidth]{figures/complexity/paper_resized.png}
    %               % \includegraphics[width=.33\textwidth]{figures/complexity/chair_resized.png}
    % % }

    % \includegraphics<2->[width=.5\textwidth]{figures/complexity/chair_resized.png}

    % \includegraphics[width=.15\textwidth]{figures/paper-unfolded.png}$\rightarrow$
    % \includegraphics[width=.15\textwidth]{figures/rhino.png}
    % \includegraphics[width=.15\textwidth]{figures/fish.png}
    % \includegraphics[width=.15\textwidth]{figures/origami-1b.png}

    % \vspace{4mm}
    % \includegraphics[width=\textwidth]{figures/hexagonflattened.png}
    % \vspace{5mm}

    % \visible<2->{
    % \includegraphics[width=\textwidth]{figures/complexity/decompose.png}
    % }

    % \visible<4->{
    %   \vspace{5mm}
    %   \includegraphics[width=\textwidth]{figures/networkTransparency.png}
    % }
  % \end{figure}
  %     \end{column}
  %   \end{columns}
  %   \end{minipage}
\end{frame}

\begin{frame}{What Does Crowdsourcing Say?}
\begin{columns}
  \begin{column}{0.6\textwidth}
    \begin{itemize}
      \item Build complexity into the process
      \begin{itemize}
        \item<1> Apply CS methods to people\\
        \scriptsize{\textcite{crowdForgeKittur}}\normalsize{}
        \item<2> Humans as computational units\\
        \scriptsize{\textcite{Lasecki:2014:LSR:2661334.2661352}}\normalsize{}
        \item<3> Crowdsourcing workflows as function state machines\\
        \scriptsize{\textcite{latoza2014microtask}
        }
      \end{itemize}
    \end{itemize}
  \end{column}

  \begin{column}{0.4\textwidth}
    \begin{figure}
    \only<1>{
    \includegraphics[width=\textwidth]{figures/complexity/cw_literature/mapReduce.png}
    }

    \only<2>{
      \includegraphics[width=\textwidth]{figures/complexity/cw_literature/scribe.png}
    }
    \only<3>{
      \begin{adjustbox}{max totalsize={\textwidth}{\textheight},center}
      \begin{tikzpicture}[->,>=stealth',auto, node distance=4cm,
                          thick,transform shape]
        \node[state,label=above:{Described}]                       (A)                    {};
        \node[state,label=left:{Described written}]                (B) [below of=A]       {};
        \node[state,label=left:{Run Tests}]                        (D) [below of=B]       {};
        \node[state,label=below:{Described written buggy}]         (C) [below right of=D] {};
        \node[state,label=below:{Described written buggy}]         (E) [below left of=D]  {};

        \path[every node/.style={sloped,anchor=south}]
              (A) edge              node {Write description} (B)
              (B) edge [loop right] node {Edit code} (B)
                  edge              node {Edit code} (D)
              (D) edge              node {} (C)
                  edge              node {} (E)
              (C) edge [bend right] node {Debug} (B)
                  edge [bend right] node {Debug} (D)
              (E) edge [bend right] node {Edit Code} (D)
                  edge [bend left]  node {Edit Code} (B);
        \end{tikzpicture}
        \end{adjustbox}
    }
    \end{figure}
  \end{column}

\end{columns}
\end{frame}

\begin{frame}{What Does Piecework Say?}
      George Airy (astronomer) used a very similar approach\\
      \scriptsize{\textcite{grier2013computers}}\normalsize{}
    \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{figures/photo/Greenwich-Observatory-computing-staff-1902.jpg}
      \end{figure}
    \end{column}

@@

\begin{frame}{Comparisons}
\begin{itemize}
  \item Limited array of tasks versus arbitrarily complex work
  \begin{itemize}
    \item \emph{Building} planes versus \emph{fixing} trains
  \end{itemize}
  \item \normalsize{Has technology changed this?}
    \begin{itemize}
      \item Technology makes \emph{some} complex tasks relatively trivial
      \item Measuring workers is easier than ever
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Complexity} % {Cab Drivers}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \only<2>{
  \begin{columns}
  \begin{column}{0.2\textwidth}
  \includegraphics[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \end{column}
  \begin{column}{0.8\textwidth}
  \includegraphics[width=\textwidth]{figures/complexity/brain_scans.png}
  \end{column}
  \end{columns}
  }
  \includegraphics<3>[width=\textwidth]{figures/photo/gps-map.jpg}
  \end{figure}
\end{frame}

\begin{frame}{Complexity} % {Algorithmic Measurement}
    notes
    \begin{itemize}
      \item I'm thinking of pointing to UpWork's screen recording tool as a way to measure workers
      \item also maybe google analytics and other ways of tracking web--based workers
    \end{itemize}
\end{frame}

\begin{frame}{Implications}
  \begin{itemize}
    \item We make stronger assumptions about workers' abilities thanks to technology
    \item Evaluation remains difficult, but we're trying to find stopgap solutions through decomposition
    \item We're still not solving the problems of inherently subjectively judged work
  \end{itemize}
\end{frame}

\onlyinsubfile{
  \printbibliography{}
}
\end{document}

>>>>

\subfile{threads}
% \againframe<2>{threads}

\begin{frame}{Complexity}
  \begin{columns}
    \begin{column}{.6\textwidth}
      \visible<-4>{What do we mean when we say \alert{complexity}?}
    \end{column}
    \begin{column}{.4\textwidth}
      \only<5->{\hfill \dots~In some cases. Sometimes.}
    \end{column}
  \end{columns}
  \begin{columns}
  \begin{column}{.55\textwidth}
  \begin{itemize}
    \item<2-> Can crowds help you \alert{revise} work?\par
    \scriptsize{\textcite{bernsteinSoylent,Kim:2014:CSI:2556288.2556986,Nebeling:2016:WCW:2858036.2858169}\par}\normalsize{}
    \item<3-> Can crowds \alert{critique} designs?\par
    \scriptsize{\textcite{yuanAlmost,fuge2014analysis}\par}\normalsize{}
    \item<4-> Can crowds create artifacts \alert{de novo}?\par
    \scriptsize{\textcite{KimStoria,Kim2017,Hahn:2016:KAB:2858036.2858364,Lasecki:2014:LSR:2661334.2661352}\par}\normalsize{}
  \end{itemize}
  \end{column}
  \begin{column}{.45\textwidth}
      \begin{itemize}
        \item[$\Rightarrow$]<6-> \hfill With variable success\par
        \visible<0>{\scriptsize{\textcite{bernsteinSoylent,Nebeling:2016:WCW:2858036.2858169}\par}\normalsize{}}
        \item[$\Rightarrow$]<7-> \hfill With careful guidance\par
        \visible<0>{\scriptsize{\textcite{yuanAlmost,fuge2014analysis}\par}\normalsize{}}
        \item[$\Rightarrow$]<8-> \hfill Within narrow specifications\par
        \visible<0>{\scriptsize{\textcite{Hahn:2016:KAB:2858036.2858364,Lasecki:2014:LSR:2661334.2661352}\par}\normalsize{}}
      \end{itemize}
  \end{column}
  \end{columns}
\end{frame}

\begin{frame}{What Does On--Demand Work Say?}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      Build complexity into the process
      \begin{itemize}
        \item<+-> Apply CS methods to people\par
                 \scriptsize{\textcite{crowdForgeKittur}\par}\normalsize{}
        \item<+-> Humans as computational units\par
                 \scriptsize{\textcite{Lasecki:2014:LSR:2661334.2661352}\par}\normalsize{}
        \item<+-> Crowdsourcing workflows as function state machines\par
                 \scriptsize{\textcite{latoza2014microtask}\par}\normalsize{}
      \end{itemize}
    \end{column}

    \begin{column}{0.4\textwidth}
      \only<1>{
      \includegraphics[max width=\textwidth,max height=\textheight]{figures/complexity/cw_literature/mapReduce.png}
      }

      \only<2>{
        \includegraphics[max width=\textwidth,max height=\textheight]{figures/complexity/cw_literature/scribe.png}
      }
      \only<3>{
        \begin{adjustbox}{max totalsize={\textwidth}{\textheight},center}
        \begin{tikzpicture}[->,>=stealth',auto, node distance=4cm,
                            thick,transform shape]
          \node[state,label=above:{Described}]                       (A)                    {};
          \node[state,label=left:{Described written}]                (B) [below of=A]       {};
          \node[state,label=left:{Run Tests}]                        (D) [below of=B]       {};
          \node[state,label=below:{Described written buggy}]         (C) [below right of=D] {};
          \node[state,label=below:{Described written buggy}]         (E) [below left of=D]  {};

          \path[every node/.style={sloped,anchor=south}]
                (A) edge              node {Write description} (B)
                (B) edge [loop right] node {Edit code} (B)
                    edge              node {Edit code} (D)
                (D) edge              node {} (C)
                    edge              node {} (E)
                (C) edge [bend right] node {Debug} (B)
                    edge [bend right] node {Debug} (D)
                (E) edge [bend right] node {Edit Code} (D)
                    edge [bend left]  node {Edit Code} (B);
          \end{tikzpicture}
          \end{adjustbox}
      }
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{What Does Piecework Say?}
  What we'll find
  \begin{itemize}
    \item<+-> Building complexity into the processes
    \item<+-> Incremental advances until managers \emph{tracked} and \emph{standardized} workers and work
    \item<+-> Insights into task specialization
  \end{itemize}
\end{frame}

\begin{frame}[t]{What Does Piecework Say?}
      George Airy (astronomer) used a very similar approach\par
      \scriptsize{\textcite{grier2013computers}\par}\normalsize{}
    \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{figure}
        \includegraphics[max width=\textwidth, max height=.7\textheight,keepaspectratio]{figures/photo/Greenwich-Observatory-computing-staff-1902.jpg}
      \end{figure}
    \end{column}

@@

\begin{frame}{Comparisons}

\begin{itemize}
    \item<+-> Building complexity into the processes
    % \item<+-> Incremental advances until managers \emph{tracked} and \emph{standardized} workers and work
    % \item<+-> Insights into task specialization
  % \end{itemize}
% \begin{itemize}
  \item Challenges dealing with flexibility
  \begin{itemize}
    \item \emph{Building} planes versus \emph{fixing} trains
  \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}{Implications for On--Demand Work}
  Has technology shifted on--demand work?
    \begin{itemize}
      \item Technology makes \emph{some} complex tasks relatively trivial
      \item Measuring workers is easier than ever
    \end{itemize}
\end{frame}

\begin{frame}{Enhanced Cognition} % {Cab Drivers}
  \begin{figure}
  \includegraphics<1>[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \only<2>{
  \begin{columns}
  \begin{column}{0.2\textwidth}
  \includegraphics[width=\textwidth]{figures/photo/knowledge-student.jpg}
  \end{column}
  \begin{column}{0.8\textwidth}
  \includegraphics[width=\textwidth]{figures/complexity/brain_scans.png}
  \end{column}
  \end{columns}
  }
  \includegraphics<3>[width=\textwidth]{figures/photo/gps-map.jpg}
  \end{figure}
\end{frame}

\begin{frame}{Tracking Work and Workers} % {Algorithmic Measurement}
    % notes
    % \begin{itemize}
      \ali{Upwork's screen recording tool as a way to measure workers}
      % \item also maybe google analytics and other ways of tracking web--based workers
    % \end{itemize}
\end{frame}

\begin{frame}{Takeaways}
  \begin{itemize}
    \item We make stronger assumptions about workers' abilities thanks to technology
    \item Evaluation remains difficult, but we're trying to find stopgap solutions through decomposition
    \item We're still not solving the problems of inherently subjectively judged work
  \end{itemize}
\end{frame}

% \onlyinsubfile{
%   \printbibliography{}
% }
\end{document}

### 2017-05-10 chi/piecework/presentation/introduction.tex
checkin with most of the bolded/critical fixes resolved (see main page)

\documentclass[presentation]{subfiles}
\onlyinsubfile{}
\setbeamersize{description width=30mm}
\begin{document}
\begin{frame}<-3>[label=returnable]{\only<-3>{Before We Get Started\dots}\only<4->{Old Wine in New Bottles}}
      \begin{description}
        \item<1-> [Crowd work] Digitally mediated \alert{information work}
        (e.g. Amazon Mechanical Turk, UpWork)\\
          \scriptsize{\textcite{crowdworkFuture}}\normalsize{}
        \item<2-> [Gig work] Digitally mediated (often \alert{physically embodied}) one--off jobs,
        such as
        \emph{driving for hire},
        \emph{courier services},
        and \emph{administrative support}\\
          \scriptsize{\textcite{friedman2014workers,Parigi:2016:GE:3026779.3013496}}\normalsize{}
        \item<3-> [On--demand~work] Crowd work and gig work, collectively
        \item<5-> [Piecework] Payment for \emph{output} rather than for \emph{time}
      \end{description}
\end{frame}

\begin{frame}[standout]
On--demand work is a modern instantiation of a much older phenomenon
--- \alert{piecework}.

@@

\againframe<4->{returnable}

\begin{frame}[t]{What is piecework?}
\centering
  \emph{Payment for \textbf{output} rather than for \textbf{time}}
\vspace*{2mm}
\begin{columns}
  \begin{column}{0.33\textwidth}
    \centering
    Textiles
    \begin{figure}
    \begin{overlayarea}{\textwidth}{33mm}
    \begin{minipage}[c][33mm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/pieceworkers.jpg}
    \end{minipage}
    \end{overlayarea}
    \end{figure}
  \end{column}
  \begin{column}{0.33\textwidth}
    \centering
    Automobiles
    \begin{figure}
    \begin{overlayarea}{\textwidth}{33mm}
    \begin{minipage}[c][33mm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/ford_assembly_line.jpg}
    \end{minipage}
    \end{overlayarea}
    \end{figure}
  \end{column}
  \begin{column}{0.33\textwidth}
    \centering
    Metalwork
    \begin{figure}
    \begin{overlayarea}{\textwidth}{33mm}
    \begin{minipage}[c][33mm]{\textwidth}
      \includegraphics[width=\textwidth]{figures/photo/Rosie_the_Riveter_(Vultee)_DS.jpg}
    \end{minipage}
    \end{overlayarea}
    \end{figure}
  \end{column}
\end{columns}

\visible<2->{
  \begin{columns}
  \centering
    \begin{column}{0.33\textwidth}
    \centering
      Crowd work
    \begin{figure}
      \begin{overlayarea}{\textwidth}{15mm}
      \begin{minipage}[c][15mm]{\textwidth}
        \includegraphics[width=\textwidth]{figures/amt.png}
      \end{minipage}
      \end{overlayarea}
    \end{figure}
    \end{column}
    \begin{column}{0.33\textwidth}
    \centering
      Gig Work
    \begin{figure}
    \begin{overlayarea}{\textwidth}{15mm}
      \begin{minipage}[c][15mm]{\textwidth}
        \includegraphics[width=\textwidth]{figures/uber.png}
      \end{minipage}
      \end{overlayarea}
    \end{figure}
    \end{column}
  \end{columns}
}

\end{frame}

% \begin{frame}{Why Piecework?}
% What makes on--demand work another instantiation of piecework?

% \ali{piecework }
% \end{frame}

@@

\begin{frame}{What will be the future of work?}
    How will \alert{technology} affect the complexity of the work that on--demand workers do?

    What are the \alert{limits} of complexity in on--demand work?
\end{frame}

@@

@@

\begin{frame}{Introduction}
  We hope to provide:
      \begin{itemize}
        \item A useful ontological lens for making sense of on--demand work as a resurgence of \alert{piecework}
        \item A method for making sense of contemporary phenomena through \alert{historical analysis}
      \end{itemize}
\end{frame}

\begin{frame}{Comparative Historical Analysis}
\begin{itemize}
  \item Historical analysis isn't new
  \begin{itemize}
    \item In general\\
    \scriptsize{\textcite{rosenberg1994exploring,rosenberg1982inside}}\normalsize{}
    \item In HCI\\
    \scriptsize{\textcite{Wyche2006,bodker1993historical}}\normalsize{}
  \end{itemize}
  \item Still, it's an underutilized method
  \begin{itemize}
    \item Provide some basic framing for \emph{ostensibly} new phenomena
    \item \emph{Explicate} our theoretical grounding
    \item Flesh out \emph{differences} and their implications
  \end{itemize}
\end{itemize}
\end{frame}

\onlyinsubfile{
  \printbibliography{}
}

>>>>

\documentclass[presentation]{subfiles}
\onlyinsubfile{}
\setbeamersize{description width=8em}
\begin{document}
\begin{frame}<-3>[label=definitions]{\only<-3>{Before We Get Started\dots}\only<4->{Old Wine in New Bottles}}
  \begin{description}
    \item<1-> [Crowd work] Digitally mediated \alert{information work}, like 
      \emph{image tagging}, \emph{audio transcription}, and \emph{data processing}\par
      \scriptsize{\textcite{crowdworkFuture}\par}\normalsize{}
    \item<2-> [Gig work] Digitally mediated (often \alert{physically embodied}) one--off jobs,
      such as
      \emph{driving for hire},
      \emph{courier services},
      and \emph{administrative support}\par
      \scriptsize{\textcite{friedman2014workers,Parigi:2016:GE:3026779.3013496}\par}\normalsize{}
    \item<3-> [On--demand work] Crowd work and gig work, collectively
  \end{description}
  \visible<5->{
     \begin{center}
        {\color{mLightBrown}
          {\begin{tikzpicture}
            \node  (C) at (0,0) {};
            \node (D) at (9,0) {};
            \path (C) to [ornament=86] (D);
          \end{tikzpicture}}}%
    \end{center}
   }
  \begin{description}
    \item<6-> [\textrm{Piecework}] \textrm{Payment for \emph{output} rather than for \emph{time}}
  \end{description}
\end{frame}

\begin{frame}[standout,label=takeaway]{}
  On--demand work is a modern instantiation of a much older phenomenon
  --- \alert{piecework}.

@@

\againframe<4->{definitions}

\begin{frame}[t]{Payment for \emph{output} rather than for \emph{time}}
  \begin{columns}[T]
    \begin{column}{0.33\textwidth}
      \centering
      Textiles\\
      \includegraphics[max width=\linewidth,max height=.3\textheight,keepaspectratio]{figures/pieceworkers.jpg}
    \end{column}
    \begin{column}{0.33\textwidth}
      \centering
      Automobiles\\
      \includegraphics[max width=\linewidth,max height=.3\textheight,keepaspectratio]{figures/photo/ford_assembly_line.jpg}
    \end{column}
    \begin{column}{0.33\textwidth}
      \centering
      Metalwork\\
      \includegraphics[max width=\linewidth,max height=.3\textheight,keepaspectratio]{figures/photo/Rosie_the_Riveter_(Vultee)_DS.jpg}
    \end{column}
  \end{columns}
  \vspace*{7mm}

  \visible<2->{
    \begin{columns}[b]
      \begin{column}[t]{0.45\textwidth}
        \centering
        Crowd work
        \begin{columns}
          \begin{column}[b]{.5\textwidth}
            \includegraphics[max width=\linewidth,max height=\textheight,keepaspectratio]{figures/amt.png}
          \end{column}
          \begin{column}[b]{.5\textwidth}
            \includegraphics[max width=\linewidth,max height=\textheight,keepaspectratio]{figures/upwork.png}
          \end{column}
        \end{columns}
      \end{column}

      \begin{column}[t]{0.45\textwidth}
        \centering
        Gig Work
        \begin{columns}
          \begin{column}{.5\textwidth}
            \includegraphics[max width=\linewidth,max height=\textheight,keepaspectratio]{figures/uber.png}
          \end{column}
          \begin{column}{.5\textwidth}
            \includegraphics[max width=\linewidth,max height=\textheight,keepaspectratio]{figures/postmates.png}
          \end{column}
        \end{columns}
      \end{column}
    \end{columns}
  }
\end{frame}

@@

\begin{frame}{What will be the future of work?}
  \begin{columns}
    \begin{column}{0.6\textwidth}
      \begin{itemize}
        \item<1-> How will \alert{technology} affect the complexity of the work that on--demand workers do?
        \item<2-> What are the \alert{limits} of complexity in on--demand work?
      \end{itemize}
    \end{column}
    \begin{column}{0.4\textwidth}
    \only<3>{
      \centering
      The answers to these questions may predict the \emph{reach} of on--demand work
    }
    \end{column}
    \end{columns}
\end{frame}

@@

\begin{frame}{Introduction}
  We hope you come away with:
      \begin{itemize}
        \item An \alert{ontological lens} for making sense of on--demand work as a resurgence of piecework
        \item A renewed interest in the use of \alert{historical analysis} to make sense of contemporary phenomena
      \end{itemize}
\end{frame}

\begin{frame}{Comparative Historical Analysis}
  HCI researchers have used historical analysis in the past\par
  \scriptsize{\textcite{Wyche2006,bodker1993historical}\par}\normalsize{}

  \dots~But we haven't applied this method to make sense of on--demand work,
        which is a missed opportunity to\dots
  \begin{itemize}
    \item Provide some basic framing for \emph{ostensibly} new phenomena
    \item \emph{Explicate} our theoretical grounding
    \item Flesh out \emph{differences} and their implications
  \end{itemize}
% \end{itemize}
\end{frame}

@@

### 2017-05-10 chi/piecework/presentation/presentation.tex
checkin presentation
checkin with most of the bolded/critical fixes resolved (see main page)

\documentclass{beamer}

\usepackage{tikz,pgf,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer,nth,xcolor,svg,subfiles,chronosys,cancel}
\usepackage{pgfcalendar}
\usepackage{datenumber,xparse,fp}

\usetikzlibrary{arrows,automata}
\usepackage[citestyle=authoryear-comp,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}

\bibliography{references}
\usetheme{metropolis}
\beamertemplatenavigationsymbolsempty
\definecolor{stanfordRed}{HTML}{8C1515}
\definecolor{metroBackground}{RGB}{250,250,250}

% Recent Notes from msb
% [ ] I suggest that you come out with a one sentence summary of your main thesis after 2 and before 3. “What I’m going to argue in this talk is that on-demand work is a modern instantiation of a much older phenomenon, piecework [put the word on the slide], and that we’re going to be able to use the history of piecework over the past two hundred years to shed light on several unanswered questions about the unfolding phenomenon of on-demand work.”
% [ ] This way people know what you’re winding up for in this talk
% [ ] don’t get rid of slide 5. I’m just saying put one framing sentence up front here.
% [ ] 3: these are not the canonical cites for complexity. kittur crowdforge is most famous
% [ ] 3: put the task hexagons at the top, not in between. the hierarchy I see what you’re trying to do, but it’s not really working
% [ ] When you introduce the piecework term, give several examples (with pictures) that listeners will be familiar with.
% [ ] You never stopped to equate piecework to on demand work. Why does piecework = on demand work? (in particular, because on demand work ALSO pays people per task)
% [ ] 3: your complexity example is being built out of triangles, not hexagons
% [ ] Get rid of the citation numbers, and replace it with years Alkhatib 2017, not Alkhatib [1]
% [ ] 3: I think this isn’t focused correctly. I’d get rid of this slide and ONLY motivate the complexity question. Then mention briefly that in the paper you also talk about decomposition and worker relationships, but you need 10 pages and 166 references rather than a 15 minute talk to do all that. Return to these other themes at the end of the talk and mention some short take aways from each one.
% [ ] 4: doesn’t make sense to ask “how will we reach those limits?”
% [ ] LOL at the phone ringing
% [ ] 7: the top timeline is events, the bottom is citations. change the bottom one to be events
% [ ] 8: this is WAY too late to still be doing an intro. You’re five minutes into the talk. Intro should be done by 2min.
% [ ] 12: the details here are irrelevant to complexity. why does it matter that they could be fired at will, overworked, underpaid? shouldn’t we be focusing on how piecework enabled the complexity? If it’s not important (as you say), then don’t include it. Parsimony, yay!
% [ ] 12: another example of a citation I can’t follow by watching slides
% [ ] 14: ditch the shrugging guy, he’s really weird
% [ ] 15: trains — this has nothing to do with complexity…? cut?
% [ ] 15: fordism — again, explain what this has to do with complexity? what does fordism have to do with complex outcomes? spell it out. what should we be learning from this?
% [ ] 16: technology makes complex tasks relatively trivial — this is an overly broad claim. makes SOME?
% [ ] 17: speed up The Knowledge/Gmaps example. I think it can go twice as fast and still carry as much weight

@@

\newenvironment{mystepwiseitemize}{\begin{itemize}[<+-| alert@+>]}{\end{itemize}}
% Theme colors are derived from these two elements
\setbeamercolor{alerted text}{fg=Orange}
\setsansfont[BoldFont={Source Sans Pro Semibold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmonofont{Source Code Pro}
\setbeamercolor{institute in head/foot}{fg=stanfordRed}
\setbeamercovered{transparent}
\setbeamercovered{again covered={\opaqueness<1->{15}}}

\title{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
% \metroset{titleformat=smallcaps}

\author{\textbf{Ali Alkhatib}, Michael Bernstein, Margaret Levi\\
\texttt{ \scriptsize{\href{mailto:ali.alkhatib@cs.stanford.edu}{ali.alkhatib@cs.stanford.edu} ||
         \href{http://twitter.com/_alialkhatib}{@\_alialkhatib}} }}

@@

\subfile{introduction}
\subfile{complexity}
\subfile{closing}
\subfile{contact}

% \begin{frame}[allowframebreaks]{References}
% \printbibliography{}
% \end{frame}

>>>>

\documentclass[aspectratio=169,12pt]{beamer} % or 14 or 17 or 20

\usepackage{tikz,pgf,lmodern,textpos,hyperref,graphicx,booktabs,appendixnumberbeamer}
\usepackage{pgfcalendar,pgfornament,svg,subfiles,chronosys,cancel,xcolor,color,nth}
\usepackage[outline]{contour}
\usepackage{datenumber,xparse,fp}
\usetikzlibrary{arrows,automata}
\usepackage[citestyle=authoryear-comp,backend=bibtex]{biblatex}
\usepackage[export]{adjustbox}
\usepackage[en-US]{datetime2}
\bibliography{references}
\usetheme{metropolis}
% \linespread{1}
% \usecolortheme{metropolis}
\beamertemplatenavigationsymbolsempty
\definecolor{stanfordRed}{HTML}{8C1515}
\definecolor{metroBackground}{RGB}{250,250,250}

% notes from last practice talk (5/9 morning):
% [x] spacing in the definitions — piecework should be more separated from the other definitions to make clearer that it's different
%      tried something different. now it's Source Serif Pro. Thoughts?
% [x] space the crowdwork and gigwork images (uber and AMT) further down to separate them from the piecework images
% [x] move the timeline to after the historical analysis slide
% [x] return to the standout slide at the end as a way of wrapping up
% [x] on that note; instead of the slide that just says "complexity", maybe take the slide with the three panels (comp, decomp, relationships) and put that in its place, and then have a transition where i gray out decomp and relationships. then at the end be like "there's a lot more in the paper, like decomposition and relationships, but we don't have time to get deeply into them. i encourage you to read the paper if you found this talk provocative [or something], as we follow a similar style for the other discussions"
% [x] there's a flickering thing that goes on in the pdf viewer i used that is super obnoxious. some other pdf viewers are less bad about it. i'm gonna trial a few viewers since i just have to go to fullscreen and click next

% [ ] slide 8: title="introduction" not good. i think i need to move all of this stuff around so this slide is earlier and i can arguably say that the timeline (slide 7) is getting into the body of the talk (all of the events correspond to advances in *complexity*, not just crowd/piecework) 
% [ ] slide 10: i can give specific examples; "soylent _revised_ academic papers; crowd research _generates new papers_" is kind of salient 
% [x] also slide 10: "from whole cloth" is both idiomatic and possibly the wrong idiom, so i'm just going to change it to something like "completely anew" or something 
% [ ] generally: need to figure out whether to keep the origami birds. they look nice but the reference to breaking tasks down into triangles and those triangles making it possible to make more complex, nuanced things is totally lost. it feels more like an inside joke that the audience won't get 
% [x] reference/explain the chart on slide 13, because i don't really explicitly reference it. it's just an image showing several people doing work, contributing to and verifying each other's work 
% [x] slide 14: farm workers need an image (mentioned before) 
% [ ] slide 16 felt super confused and foggy. maybe it was just too abrupt. i'll try to practice my transition to it 
% [ ] slide 17: i'm dropping figure B and maybe the tiny image on the left. sound okay? 
% [ ] slide 18: needs real content and not just internal notes 
% [x] slide 20: i actually left out the relationships panel. also no visualizations. thoughts? 
% [x] slide 21: it's not twofold if i have 3 things -_- 
% [ ] slide 22: "thanks and questions?"

% more of MSB's notes
% !!!!!! [x] spend a little more time motivating why the complexity question is important. If we knew the answer to this, we would be able to predict what kind of worker displacements might happen, build appropriate infrastructure, create strong worker advocate groups, etc. 
% !!!!!! [x] 11: I think this needs to be bounded. you need to argue that in fact NOT ALL complex stuff has been achieved. e.g., the three examples you gave, while we’ve made progress, are basically still open questions. and are they fundamentally impossible, or just facing a lack of engineering imagination? that’s what we turn to piecework to answer. <— important transition, it frames the question
% !!!!!! [x] I need to hear the argument that you’re going to make about what piecework has to say about complexity, before you dive into the “ hat does piecework say?" history. otherwise it feels like a wandering tour rather than an argument.
% !!!!!! [ ] Slide 20: instead of just handwaving that we talk about it, summarize the big takeaways from your Table 1. e.g., "Decomposition: After scientific management matured, piecework began specialized training to create experts in narrow tasks. A similar shift seems feasible with on–demand work.” and “Relationships: While worker frustrations are similar, the decentralized nature of on–demand work will limit collective action until there exist platforms to coordinate and exert pressure.”
% [x] Don’t introduce your name and title; the session chair will do that for you. Make sure to show up to the room in the break before your session (at least 15min early) to test your laptop and introduce yourself to the session chair
% [x] 2: Upwork, not UpWork
% [x] 2: top bullet is services, bottom is categories. make them consistent
% [x] Intro is way better now. congrats!
% [ ] On final slide, thank Stanford Cyber Initiative for funding
% [ ] First half of Slide 8 seems redundant. Cut? And just focus on the second half.
% [ ] 10: wrap this together — essentially you need to say “so this reduces to a question of what can, and what can’t be crowdsourced. What are the limits, if any?” and put something like that on the slide
% [x] 11: inconsistent language use in titles, for example “crowdsorucing” instead of “on-demand work” in the title? unless this is intentional
% [ ] (by the time you get to automobiles, I don’t know why you’re telling me what you’re telling me)
% [ ] 13: not clear how ascention and descention of stars is “in the process”. I suggest pointing out instead that he reduced it to simple addition etc calculations that people passed between each other
% [ ] I don’t know what “marginal complexity” means. Either explain it or change the term
% [ ] 15: change “values” to “payment”…clearer
% [ ] 16 or after: make clear that technology hasn’t fundamentally changed the relationship. we can still do the equivalent of building planes, and still can’t do the equivalent of fixing planes (things that require breadth of knowledge and flexibility)
% [x] 17: don’t spend time laying out the dual hypotheses. just say that clearly this is either causing changes in the brain, or selecting for a small subset of people (in one sentence) — either way not a complex task that just anyone can do
% [ ] 21: be clear on the slide bullet three that this is about History as a lens on contemporary phenomena. right now it’s not clear

@@

\newenvironment{mystepwiseitemize}{\begin{itemize}[<+-| alert@+>]}{\end{itemize}}
% Theme colors are derived from these two elements
\setbeamercolor{alerted text}{fg=Orange}
\setsansfont[BoldFont={Source Sans Pro Bold},
              Numbers={OldStyle}]{Source Sans Pro}
\setmainfont[BoldFont={Source Serif Pro Semibold},
              Numbers={OldStyle}]{Source Serif Pro}
\setmonofont{Source Code Pro}
\setbeamercolor{institute in head/foot}{fg=stanfordRed}
\setbeamercovered{transparent}
\setbeamercovered{again covered={\opaqueness<1->{15}}}

\title{Examining Crowd Work and Gig Work Through The Historical Lens of Piecework}
% \metroset{titleformat=smallcaps}
\contourlength{0.1pt}
\contournumber{10}
\author{\textbf{Ali Alkhatib}, Michael Bernstein, Margaret Levi\\
\texttt{ \scriptsize{\href{mailto:ali.alkhatib@cs.stanford.edu}{ali.alkhatib@cs.stanford.edu} ||
         \href{http://twitter.com/_alialkhatib}{@\_alialkhatib}}\normalsize{} }}

@@

\subfile{introduction}
\subfile{complexity}
\subfile{closing}
\againframe[standout]{takeaway}
\subfile{contact}

\begin{frame}[allowframebreaks]{References}
  \printbibliography{}
\end{frame}
